### 2018-09-03 Manuscripts/cog-psych/revision/cogpsych.tex
Need to investigate source of weird corr fits.

PACKER sets $f(x_j)$ depending on exemplar $x_j$'s category membership:
$f(x_j) = \theta_t$ if $x_j$ is a member of the target category, and
$f(x_j) = -\theta_c$ if $x_j$ is a member of a contrast category.
$\theta_t$ and $\theta_c$ are free parameters
($0 \leq (\theta_t,\theta_c) \leq 1$) controlling the trade-off
between within- and between-category similarity. For example, when
$\theta_t = \theta_c = 0.5$, $f(x_j) = 0.5$ for members of the
target category and $f(x_j) = -0.5$ for members of other categories; thus, the
model is likely to generate items that are similar to members of the target
category but are not similar to members of other categories. In this way,
$\theta_t > 0$ with $\theta_c = 0$ produces exclusive consideration
of target-category members, and $\theta_c > 0$ with $\theta_t = 0$
produces exclusive consideration of contrast-category members. The combination
of $\theta_t$ and $\theta_c$ parameters thus specifies a wide
breadth of possible approaches; by fitting it to a dataset, one can describe the
relative roles of between-category contrast and within-category similarity in
generation. See Figure \ref{fig:packer-examples} for an illustration of how
these parameters control the relative influence of within-category similarity
and contrast to other categories when generating a new exemplar.

@@

Despite both the original hierarchical Bayesian model and our representativeness
model sharing identical hierarchical structures, their distinct response
processes can yield very different exemplars. Specifically, the hierarchical
Bayesian model emphasizes the generation of exemplars that maintain
distributional commonalities across categories. In contrast, the
representativeness model focuses on the generation of exemplars that are
representative of the underlying distribution for a target category. Generally,
this representativeness mechanism results in the generation of exemplars that
are less similar (i.e., more different) to contrast categories. We see this
illustrated in Figure \ref{fig:representative-examples}, where the
representativeness model displays a strong preference for generating exemplars
from target category 'B' that are further away from the contrast category 'A'.

@@

In addition to demonstrating the utility of formal modeling in the study
creative cognition, the PACKER model more specifically offers an additional
interpretation of some of the field's most central findings. For example,
perhaps the most foundational principle from this literature concerns the
limiting influence of prior knowledge: Individuals create new categories
composed of features from existing classes, and what is created can be
influenced drastically through the introduction of cues or examples
\citep{marsh1999inadvertent,smith1993constraining}. In this paper, we have
identified another important aspect of the constraining influence of prior
knowledge: What is generated cannot be the same as what is already known.
Further, there is systematicity in how generated categories differ from prior
knowledge. The results of our simulations with PACKER demonstrate that this
influence is concisely explained in terms of a trade-off between within-category
similarity and between-category dissimilarity.

Similarly, PACKER may offer an additional interpretation of existing accounts of
creative generation. Most notably, a leading account within the creative
cognition literature, the Path of Least Resistance
\citep{ward1994structured,ward1995s}, also explains generation in terms of an
exemplar-based retrieval process. This account was designed to explain the
creative generation of natural categories (e.g., new species of plants and
animals) and as a result relies strongly on the hierarchical organization of
these categories: Individuals are thought to retrieve an example of the
higher-level category being generated (e.g., \textit{bird} may be retrieved from
the category \textit{animal}), and then systematically alter what was retrieved
to make something new. As the PACKER model does not assume knowledge is
hierarchically organized \citep[this is true of the exemplar view more broadly,
see][]{murphy2016exemplar}, the model may be viewed as a formal instantiation of
the Path of Least Resistance for application in a traditional artificial
categorization domain (when there is no established hierarchy of categories).
PACKER's success in explaining generation within an artificial domain motivates
future work exploring the nature of category contrast within a more naturalistic
setting.

@@

\subsection{Exemplar dissimilarity and Representativeness in Categorization}

@@

>>>>

PACKER sets $f(x_j)$ depending on exemplar $x_j$'s category membership:
$f(x_j) = \theta_t$ if $x_j$ is a member of the target category, and
$f(x_j) = -\theta_c$ if $x_j$ is a member of a contrast category. $\theta_t$ and
$\theta_c$ are free parameters ($0 \leq \theta_t,\theta_c$) controlling the
trade-off between within- and between-category similarity. For example, when
$\theta_t = \theta_c = 0.5$, $f(x_j) = 0.5$ for members of the target category
and $f(x_j) = -0.5$ for members of other categories; thus, the model is likely
to generate items that are similar to members of the target category but are not
similar to members of other categories. In this way, $\theta_t > 0$ with
$\theta_c = 0$ produces exclusive consideration of target-category members, and
$\theta_c > 0$ with $\theta_t = 0$ produces exclusive consideration of
contrast-category members. The combination of $\theta_t$ and $\theta_c$
parameters thus specifies a wide breadth of possible approaches; by fitting it
to a dataset, one can describe the relative roles of between-category contrast
and within-category similarity in generation. See Figure
\ref{fig:packer-examples} for an illustration of how these parameters control
the relative influence of within-category similarity and contrast to other
categories when generating a new exemplar.

@@

Despite both the original hierarchical Bayesian model and our representativeness
model sharing identical hierarchical structures, their distinct response
processes can yield very different exemplars. Specifically, the hierarchical
Bayesian model emphasizes the generation of exemplars that maintain
distributional commonalities across categories. In contrast, the
representativeness model focuses on the generation of exemplars that are
representative of the underlying distribution for a target category. Generally,
this mechanism of representativeness results in the generation of exemplars that
are less similar to exemplars from other categories. We see this illustrated in
Figure \ref{fig:representative-examples}, where the representativeness model
displays a strong preference for generating exemplars from target category 'B'
that are further away from the contrast category 'A'.

@@

In addition to demonstrating the utility of formal modeling in the study
creative cognition, the contrast models more specifically offer an additional
interpretation of some of the field's most central findings. For example,
perhaps the most foundational principle from this literature concerns the
limiting influence of prior knowledge: Individuals create new categories
composed of features from existing classes, and what is created can be
influenced drastically through the introduction of cues or examples
\citep{marsh1999inadvertent,smith1993constraining}. In this paper, we have
identified another important aspect of the constraining influence of prior
knowledge: What is generated tends to be different to what is already known.
Further, there is systematicity in how generated categories differ from prior
knowledge. The results of our simulations suggest that this conceptualization of
difference can be addressed in at least two different ways. Specifically,
simulations with PACKER demonstrate that the constraining influence of
difference is concisely explained in terms of a trade-off between
within-category similarity and between-category dissimilarity. Conversely, the
representativeness model shows that this influence can also be the result of
enhancing the representativeness of generated exemplars to their category. [xian edit]

PACKER may offer an additional interpretation of existing accounts of creative
generation. Most notably, a leading account within the creative cognition
literature, the Path of Least Resistance \citep{ward1994structured,ward1995s},
also explains generation in terms of an exemplar-based retrieval process. This
account was designed to explain the creative generation of natural categories
(e.g., new species of plants and animals) and as a result relies strongly on the
hierarchical organization of these categories: Individuals are thought to
retrieve an example of the higher-level category being generated (e.g.,
\textit{bird} may be retrieved from the category \textit{animal}), and then
systematically alter what was retrieved to make something new. As the PACKER
model does not assume knowledge is hierarchically organized \citep[this is true
of the exemplar view more broadly, see][]{murphy2016exemplar}, the model may be
viewed as a formal instantiation of the Path of Least Resistance for application
in a traditional artificial categorization domain (when there is no established
hierarchy of categories). PACKER's success in explaining generation within an
artificial domain motivates future work exploring the nature of category
contrast within a more naturalistic setting.

@@

\subsection{Disentangling Exemplar dissimilarity and Representativeness in Categorization}

@@

In this paper, we have developed two novel models of category generation, each
involving a different conceptualization of contrast.  However, there is no theoretical constraint that dictates the It is also possible to treat the similarity

A thorough investigation to disentangle the two contrast mechanisms here is
beyond the scope of the current article. However, as a quick proof of concept it
is useful to check if the addition of a representativeness mechanism to an
exemplar model would yield any benefit at all.
